Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-04-01 paper/07-experiment.tex
new scripts for 1x1 and nxn

\section{Implementation and Experiments}

\subsection{Experimental Methodology}

@@

\begin{figure}[!t]
\centering
  \subfigure[Throughput. Content packet size: 1024 bytes]{\includegraphics[width=1.5in]{images/throughput_1024.pdf}\label{1a}}
  \hfil
  \subfigure[Throughput. Content packet size: 10240 bytes]{\includegraphics[width=1.5in]{images/throughput_10240.pdf}\label{1b}}
  \hfil
  \subfigure[RTT. Content packet size: 1024 bytes]{\includegraphics[width=1.5in]{images/rtt_1024.pdf}\label{1c}}
  \hfil
  \subfigure[RTT. Content packet size: 10240 bytes]{\includegraphics[width=1.5in]{images/rtt_10240.pdf}\label{1d}}

\caption{Throughput per consumer. 1 Producer X N consumers. Content packet size: 1024B}\label{exp1}
\end{figure}

>>>>

\section{Performance Evaluation}

\subsection{Implementation}

\subsection{Experiments}

@@

\begin{figure}[]
\centering
  \subfigure[Throughput]{\includegraphics[width=0.49\textwidth]{images/1_1_thput.pdf}\label{1a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.49\textwidth]{images/1_1_rtt.pdf}\label{1b}}
\caption{CCVPN performance with one consumer and one producer for increasing interest issuance rates.}\label{exp1}
\end{figure}
